---
title: "220 Project"
author: "Alex Fan"
date: "11/25/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r}
library(readr)
library(tidyverse)
library(stargazer)
dat <- read_csv("dat.csv")
```

# Clean the data and make model spec. variables
```{r}
head(dat)

dat$age2 <- dat$age^2
dat$srvlng2 <- dat$srvlng^2
dat$rgroup <- factor(dat$rgroup)
prop.table(table(dat$rgroup))
levels(dat$rgroup) <- c("None", "Protestant", "Catholic", "Other Christian", "Other religion")
dat$rgroup <- factor(dat$rgroup, levels = c("Protestant", "None", "Catholic", "Other Christian", "Other religion"))

```

# Model with NOW data
```{r}
datNOW <- dat %>%
  filter(congress == 105)

lm.1 <- lm(nowtot ~ ngirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + factor(totchi) + factor(region), data = datNOW)
summary(lm.1)
```

# Model with AAUW 105th Congress
```{r}
datAAUW105 <- dat %>%
  filter (congress == 105)
lm.2 <- lm(aauw ~ ngirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + factor(totchi) + factor(region), data = datAAUW105)
summary(lm.2)
```

# Model with AAUW 106th Congress
```{r}
datAAUW106 <- dat %>%
  filter (congress == 106)
lm.3 <- lm(aauw ~ ngirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + factor(totchi) + factor(region), data = datAAUW106)
summary(lm.3)
```

# Model with AAUW 107th Congress
```{r}
datAAUW107 <- dat %>%
  filter (congress == 107)
lm.4 <- lm(aauw ~ ngirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + factor(totchi) + factor(region), data = datAAUW107)
summary(lm.4)
```

# Model with AAUW 107th Congress
```{r}
datAAUW108 <- dat %>%
  filter (congress == 108)
lm.5 <- lm(aauw ~ ngirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + factor(totchi) + factor(region), data = datAAUW108)
summary(lm.5)
```

# Put all models in a stargazer table
```{r, results = "hide"}
stargazer(lm.1, lm.2, lm.3, lm.4, lm.5, title = "Table 2—Impact of Female Children on Legislator Voting on Women’s Issues")
```

\begin{table}[!htbp] \centering 
  \caption{Replication of Table 2—Impact of Female Children on Legislator Voting on Women’s Issues} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{5}{c}{\textit{Dependent variable:}} \\ 
\cline{2-6} 
\\[-1.8ex] & NOW & \multicolumn{4}{c}{AAUW} \\ 
\\[-1.8ex] & 105th & 105th & 106th & 107th & 108th \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5)\\ 
\hline \\[-1.8ex] 
 Number of female children & 2.300$^{**}$ & 2.385$^{**}$ & 1.688 & 2.421$^{**}$ & 2.250$^{*}$ \\ 
  & (1.038) & (1.124) & (1.136) & (1.092) & (1.145) \\ 
  & & & & & \\ 
 Female & 10.838$^{***}$ & 9.194$^{***}$ & 10.440$^{***}$ & 7.564$^{***}$ & 6.909$^{**}$ \\ 
  & (2.690) & (2.910) & (2.881) & (2.618) & (2.730) \\ 
  & & & & & \\ 
 White & 1.860 & 0.144 & 2.594 & $-$2.626 & 1.939 \\ 
  & (3.451) & (3.676) & (3.833) & (3.150) & (3.211) \\ 
  & & & & & \\ 
 Republican & $-$44.903$^{***}$ & $-$60.468$^{***}$ & $-$55.927$^{***}$ & $-$63.216$^{***}$ & $-$63.932$^{***}$ \\ 
  & (2.109) & (2.280) & (2.335) & (2.120) & (2.436) \\ 
  & & & & & \\ 
 Age & 0.661 & 0.854 & 2.034$^{**}$ & 1.298 & 2.300$^{***}$ \\ 
  & (0.800) & (0.860) & (0.902) & (0.799) & (0.860) \\ 
  & & & & & \\ 
 Age squared & $-$0.006 & $-$0.006 & $-$0.018$^{**}$ & $-$0.012 & $-$0.021$^{**}$ \\ 
  & (0.008) & (0.008) & (0.009) & (0.007) & (0.008) \\ 
  & & & & & \\ 
 Service Length & 0.235 & $-$0.208 & $-$0.726$^{*}$ & $-$0.100 & $-$0.139 \\ 
  & (0.300) & (0.324) & (0.380) & (0.346) & (0.327) \\ 
  & & & & & \\ 
 Service length squared & $-$0.009 & 0.004 & 0.025$^{*}$ & $-$0.0002 & 0.004 \\ 
  & (0.010) & (0.011) & (0.013) & (0.011) & (0.010) \\ 
  & & & & & \\ 
 No religion & 7.262 & 5.671 & 5.353 & 7.027 & $-$7.137 \\ 
  & (7.022) & (7.606) & (7.791) & (7.176) & (7.499) \\ 
  & & & & & \\ 
 Catholic & $-$3.974$^{**}$ & $-$4.505$^{**}$ & $-$2.277 & $-$4.016$^{**}$ & $-$5.468$^{***}$ \\ 
  & (1.941) & (2.091) & (2.129) & (1.987) & (2.077) \\ 
  & & & & & \\ 
 Other Christian & 0.769 & 3.204 & 1.690 & 1.646 & 3.874 \\ 
  & (4.600) & (4.983) & (4.912) & (4.491) & (4.684) \\ 
  & & & & & \\ 
 Other religion & 10.866$^{***}$ & 9.683$^{**}$ & 11.890$^{***}$ & 10.286$^{***}$ & 3.156 \\ 
  & (3.752) & (4.047) & (4.343) & (3.785) & (3.959) \\ 
  & & & & & \\ 
 Democratic vote share in district & 84.158$^{***}$ & 62.148$^{***}$ & 57.437$^{***}$ & 56.206$^{***}$ & 66.950$^{***}$ \\ 
  & (10.869) & (11.568) & (12.018) & (9.092) & (10.889) \\ 
  & & & & & \\ 
\hline \\[-1.8ex] 
N & 430 & 434 & 434 & 434 & 433 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

# Table 3 Replication
## NOW all legislators
```{r}
lm_all_NOW<-lm(nowtot~ngirls + female + white + repub + age + age2 + srvlng + srvlng2+ rgroup + demvote + factor(totchi) + factor(region),data=datNOW)
lm_all_NOW$coefficients[2]
```

## NOW Men only
```{r}
lm_men_NOW <- lm(nowtot~ngirls + female + white + repub + age + age2 + srvlng + srvlng2+ rgroup + demvote + factor(totchi) + factor(region),data=datNOW, subset=female==0)
lm_men_NOW$coefficients[2]
```

## NOW Women only
```{r}
lm_women_NOW <- lm(nowtot~ngirls + female + white + repub + age + age2 + srvlng + srvlng2+ rgroup + demvote + factor(totchi) + factor(region),data=datNOW, subset=female==1)
lm_women_NOW$coefficients[2]
```

## NOW Dems only
```{r}
lm_Dem_NOW <- lm(nowtot~ngirls + female + white + repub + age + age2 + srvlng + srvlng2+ rgroup + demvote + factor(totchi) + factor(region),data=datNOW, subset=repub==0)
lm_Dem_NOW$coefficients[2]
```

## NOW Repubs only
```{r}
lm_Repub_NOW <- lm(nowtot~ngirls + female + white + repub + age + age2 + srvlng + srvlng2+ rgroup + demvote + factor(totchi) + factor(region),data=datNOW, subset=repub==1)
lm_Repub_NOW$coefficients[2]
```

## AAUW All
```{r}
lm_all_AAUW <- lm(aauw~ngirls + female + white + repub + age + age2 + srvlng + srvlng2+ rgroup + demvote + factor(totchi) + factor(region),data=datAAUW105)
lm_all_AAUW$coefficients[2]
```

## AAUW Men only
```{r}
lm_men_AAUW <- lm(aauw~ngirls + female + white + repub + age + age2 + srvlng + srvlng2+ rgroup + demvote + factor(totchi) + factor(region),data=datAAUW105, subset = female == 0)
lm_men_AAUW$coefficients[2]
```

## AAUW Women only
```{r}
lm_women_AAUW <- lm(aauw~ngirls + female + white + repub + age + age2 + srvlng + srvlng2+ rgroup + demvote + factor(totchi) + factor(region),data=datAAUW105, subset = female == 1)
lm_women_AAUW$coefficients[2]
```

## AAUW Dems only
```{r}
lm_Dem_AAUW <- lm(aauw~ngirls + female + white + repub + age + age2 + srvlng + srvlng2+ rgroup + demvote + factor(totchi) + factor(region),data=datAAUW105, subset = repub == 0)
lm_Dem_AAUW$coefficients[2]
```

## AAUW Repubs only
```{r}
lm_Repub_AAUW <- lm(aauw~ngirls + female + white + repub + age + age2 + srvlng + srvlng2+ rgroup + demvote + factor(totchi) + factor(region),data=datAAUW105, subset = repub == 1)
lm_Repub_AAUW$coefficients[2]
```

## Make the table

\begin{table}[!htbp] \centering 
  \caption{Replication of Table 3—Impact of Female Children on Legislator Voting on Women’s Issues, by Legislator Gender and Party} 
  \label{} 
  \textit{(Each cell presents the coefficient on number of daughters from a different regression)}
\begin{tabular}{lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
& & \multicolumn{2}{c}{\textit{Gender}} & \multicolumn{2}{c}{\textit{Party}} \\ 
\\[-1.8ex] Data Source & All Legislators & Men & Women & Democrats & Republicans \\ 
\hline \\[-1.8ex] 
 NOW, 105th Congress & 2.3$^{**}$ & 2.48$^{**}$ & -1.67 & 2.93$^{*}$ & 1.28$^{*}$ \\ 
  & (1.04) & (1.09) & (5.64) & (1.6) & (1.32) \\ 
  & [430] & [382] & [48] & [204] & [226] \\
  & & & & & \\ 
 AAUW, 105th Congress & 2.38$^{**}$ & 2.49$^{**}$ & -3.9 & 2.22 & 1.83 \\ 
  & (1.12) & (1.17) & (6.41) & (1.44) & (1.56) \\ 
  & [434] & [386] & [48] & [207] & [227] \\
  & & & & & \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

# Extensions

## Ext2: Use whether ever having a female child instead of number of female children.
```{r, results = 'hide'}
lm_ext2_105 <-lm(aauw ~ anygirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + factor(totchi) + factor(region) , data = datAAUW105)
lm_ext2_106 <-lm(aauw ~ anygirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + factor(totchi) + factor(region) , data = datAAUW106)
lm_ext2_107 <-lm(aauw ~ anygirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + factor(totchi) + factor(region) , data = datAAUW107)
lm_ext2_108 <-lm(aauw ~ anygirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + factor(totchi) + factor(region) , data = datAAUW108)

summary(lm_ext2_105)
summary(lm_ext2_106)
summary(lm_ext2_107)
summary(lm_ext2_108)
stargazer(lm_ext2_105, lm_ext2_106, lm_ext2_107, lm_ext2_108)
```

\begin{table}[!htbp] \centering 
  \caption{Impact of Having Any Female Children on Legislator Voting on Women’s Issues} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{AAUW} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Has Female Child & 4.400$^{*}$ & 3.252 & 2.318 & 1.609 \\ 
  & (2.661) & (2.565) & (2.396) & (2.468) \\ 
  & & & & \\ 
 Female & 9.174$^{***}$ & 10.456$^{***}$ & 7.503$^{***}$ & 6.907$^{**}$ \\ 
  & (2.918) & (2.883) & (2.631) & (2.743) \\ 
  & & & & \\ 
 White  & 0.035 & 2.538 & $-$2.744 & 1.794 \\ 
  & (3.683) & (3.837) & (3.165) & (3.226) \\ 
  & & & & \\ 
 Republican & $-$60.542$^{***}$ & $-$56.008$^{***}$ & $-$63.410$^{***}$ & $-$63.919$^{***}$ \\ 
  & (2.285) & (2.337) & (2.129) & (2.448) \\ 
  & & & & \\ 
 Age & 0.834 & 2.001$^{**}$ & 1.353$^{*}$ & 2.312$^{***}$ \\ 
  & (0.863) & (0.903) & (0.803) & (0.864) \\ 
  & & & & \\ 
 Age squared & $-$0.006 & $-$0.018$^{**}$ & $-$0.012 & $-$0.021$^{**}$ \\ 
  & (0.008) & (0.009) & (0.007) & (0.008) \\ 
  & & & & \\ 
 Service Length & $-$0.239 & $-$0.748$^{*}$ & $-$0.092 & $-$0.127 \\ 
  & (0.324) & (0.381) & (0.349) & (0.328) \\ 
  & & & & \\ 
 Service Length squared & 0.004 & 0.026$^{**}$ & $-$0.001 & 0.004 \\ 
  & (0.011) & (0.013) & (0.011) & (0.010) \\ 
  & & & & \\ 
 No Religion & 5.492 & 4.782 & 6.681 & $-$7.286 \\ 
  & (7.626) & (7.804) & (7.221) & (7.541) \\ 
  & & & & \\ 
 Catholic & $-$4.613$^{**}$ & $-$2.323 & $-$3.969$^{**}$ & $-$5.356$^{**}$ \\ 
  & (2.095) & (2.130) & (1.997) & (2.085) \\ 
  & & & & \\ 
 Other Christian & 3.085 & 1.336 & 1.136 & 3.422 \\ 
  & (4.998) & (4.932) & (4.516) & (4.707) \\ 
  & & & & \\ 
 Other religion & 9.506$^{**}$ & 11.705$^{***}$ & 10.274$^{***}$ & 3.278 \\ 
  & (4.059) & (4.345) & (3.805) & (3.976) \\ 
  & & & & \\ 
 Democrative vote share in district & 62.510$^{***}$ & 57.591$^{***}$ & 56.325$^{***}$ & 67.648$^{***}$ \\ 
  & (11.594) & (12.025) & (9.148) & (10.962) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 434 & 434 & 434 & 433 \\ 
R$^{2}$ & 0.839 & 0.814 & 0.864 & 0.857 \\ 
Adjusted R$^{2}$ & 0.827 & 0.800 & 0.853 & 0.846 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 

## Ext3: Use proportion of female children instead of number of female children
```{r, results = 'hide'}
lm_ext3_105 <-lm(aauw ~ propgirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + factor(totchi) + factor(region) , data = datAAUW105)
lm_ext3_106 <-lm(aauw ~ propgirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + factor(totchi) + factor(region) , data = datAAUW106)
lm_ext3_107 <-lm(aauw ~ propgirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + factor(totchi) + factor(region) , data = datAAUW107)
lm_ext3_108 <-lm(aauw ~ propgirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + factor(totchi) + factor(region) , data = datAAUW108)

summary(lm_ext3_105)
summary(lm_ext3_106)
summary(lm_ext3_107)
summary(lm_ext3_108)
stargazer(lm_ext3_105, lm_ext3_106, lm_ext3_107, lm_ext3_108)
```

\begin{table}[!htbp] \centering 
  \caption{Impact of the Proportion of Female Children on Legislator Voting on Women’s Issues} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{AAUW} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Proportion of Girls & 6.922$^{**}$ & 4.764$^{*}$ & 4.728$^{*}$ & 4.110 \\ 
  & (2.907) & (2.847) & (2.645) & (2.749) \\ 
  & & & & \\ 
 Female & 9.284$^{***}$ & 10.563$^{***}$ & 7.643$^{***}$ & 6.995$^{**}$ \\ 
  & (2.905) & (2.879) & (2.625) & (2.737) \\ 
  & & & & \\ 
 White & $-$0.035 & 2.389 & $-$2.737 & 1.760 \\ 
  & (3.670) & (3.833) & (3.156) & (3.218) \\ 
  & & & & \\ 
 Republican & $-$60.373$^{***}$ & $-$55.879$^{***}$ & $-$63.251$^{***}$ & $-$63.936$^{***}$ \\ 
  & (2.278) & (2.334) & (2.124) & (2.441) \\ 
  & & & & \\ 
 Age & 0.876 & 2.056$^{**}$ & 1.354$^{*}$ & 2.307$^{***}$ \\ 
  & (0.859) & (0.901) & (0.800) & (0.862) \\ 
  & & & & \\ 
 Age squared & $-$0.007 & $-$0.019$^{**}$ & $-$0.012 & $-$0.021$^{**}$ \\ 
  & (0.008) & (0.008) & (0.007) & (0.008) \\ 
  & & & & \\ 
 Service Length & $-$0.227 & $-$0.747$^{*}$ & $-$0.114 & $-$0.136 \\ 
  & (0.323) & (0.380) & (0.347) & (0.327) \\ 
  & & & & \\ 
 Service Length squared & 0.004 & 0.026$^{**}$ & 0.0002 & 0.004 \\ 
  & (0.011) & (0.013) & (0.011) & (0.010) \\ 
  & & & & \\ 
 No religion & 5.665 & 5.135 & 6.803 & $-$7.274 \\ 
  & (7.595) & (7.785) & (7.193) & (7.516) \\ 
  & & & & \\ 
 Catholic & $-$4.535$^{**}$ & $-$2.250 & $-$3.937$^{**}$ & $-$5.412$^{***}$ \\ 
  & (2.088) & (2.127) & (1.991) & (2.081) \\ 
  & & & & \\ 
 Other Christian & 3.213 & 1.510 & 1.338 & 3.618 \\ 
  & (4.976) & (4.912) & (4.498) & (4.691) \\ 
  & & & & \\ 
 Other religion & 9.781$^{**}$ & 11.955$^{***}$ & 10.331$^{***}$ & 3.239 \\ 
  & (4.042) & (4.340) & (3.793) & (3.967) \\ 
  & & & & \\ 
 Democrative vote in district & 62.280$^{***}$ & 57.199$^{***}$ & 56.133$^{***}$ & 67.071$^{***}$ \\ 
  & (11.551) & (12.013) & (9.116) & (10.920) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 434 & 434 & 434 & 433 \\ 
R$^{2}$ & 0.840 & 0.815 & 0.864 & 0.858 \\ 
Adjusted R$^{2}$ & 0.828 & 0.801 & 0.854 & 0.847 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 

## Ext4: Add an interaction term between “girls” and female representatives.
```{r, results = 'hide'}
lm_ext4_105 <-lm(aauw ~ ngirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + ngirls*female + factor(totchi) + factor(region) , data = datAAUW105)
lm_ext4_106 <-lm(aauw ~ ngirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + ngirls*female + factor(totchi) + factor(region) , data = datAAUW106)
lm_ext4_107 <-lm(aauw ~ ngirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + ngirls*female + factor(totchi) + factor(region) , data = datAAUW107)
lm_ext4_108 <-lm(aauw ~ ngirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + ngirls*female + factor(totchi) + factor(region) , data = datAAUW108)

summary(lm_ext4_105)
summary(lm_ext4_106)
summary(lm_ext4_107)
summary(lm_ext4_108)
stargazer(lm_ext4_105, lm_ext4_106, lm_ext4_107, lm_ext4_108)
```

\begin{table}[!htbp] \centering 
  \caption{Impact of Number of Female Children on Legislator's Women's Issues Voting Record (including interaction b/w number of female children and sex of legislator)} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{AAUW} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Number of female children & 2.530$^{**}$ & 1.123 & 2.110$^{*}$ & 2.082$^{*}$ \\ 
  & (1.165) & (1.180) & (1.133) & (1.193) \\ 
  & & & & \\
 Number of female children$*$female & $-$1.272 & 4.369$^{*}$ & 2.487 & 1.260 \\ 
  & (2.671) & (2.547) & (2.429) & (2.476) \\ 
  & & & & \\ 
 Female & 10.924$^{**}$ & 4.950 & 4.886 & 5.517 \\ 
  & (4.657) & (4.301) & (3.700) & (3.866) \\ 
  & & & & \\ 
 White & 0.328 & 1.994 & $-$2.975 & 1.804 \\ 
  & (3.700) & (3.840) & (3.168) & (3.224) \\ 
  & & & & \\ 
 Republican & $-$60.434$^{***}$ & $-$55.997$^{***}$ & $-$63.167$^{***}$ & $-$63.955$^{***}$ \\ 
  & (2.284) & (2.330) & (2.120) & (2.439) \\ 
  & & & & \\ 
 Age & 0.833 & 2.100$^{**}$ & 1.394$^{*}$ & 2.333$^{***}$ \\ 
  & (0.862) & (0.900) & (0.804) & (0.863) \\ 
  & & & & \\ 
 Age squared & $-$0.006 & $-$0.019$^{**}$ & $-$0.012$^{*}$ & $-$0.021$^{***}$ \\ 
  & (0.008) & (0.008) & (0.008) & (0.008) \\ 
  & & & & \\ 
 Service Length & $-$0.200 & $-$0.741$^{*}$ & $-$0.133 & $-$0.149 \\ 
  & (0.324) & (0.379) & (0.347) & (0.327) \\ 
  & & & & \\ 
 Service Length squared & 0.003 & 0.026$^{**}$ & 0.001 & 0.005 \\ 
  & (0.011) & (0.013) & (0.011) & (0.010) \\ 
  & & & & \\ 
 No religion & 5.510 & 6.552 & 7.643 & $-$6.869 \\ 
  & (7.621) & (7.803) & (7.201) & (7.525) \\ 
  & & & & \\ 
 Catholic & $-$4.549$^{**}$ & $-$2.136 & $-$3.856$^{*}$ & $-$5.428$^{***}$ \\ 
  & (2.095) & (2.125) & (1.993) & (2.081) \\ 
  & & & & \\ 
 Other Christian & 3.132 & 1.732 & 1.819 & 3.994 \\ 
  & (4.990) & (4.900) & (4.494) & (4.694) \\ 
  & & & & \\ 
 Other religion & 9.677$^{**}$ & 12.284$^{***}$ & 10.596$^{***}$ & 3.258 \\ 
  & (4.051) & (4.338) & (3.797) & (3.968) \\ 
  & & & & \\ 
 Democrative vote in district & 62.512$^{***}$ & 56.569$^{***}$ & 55.796$^{***}$ & 66.884$^{***}$ \\ 
  & (11.604) & (11.999) & (9.100) & (10.900) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 434 & 434 & 434 & 433 \\ 
R$^{2}$ & 0.840 & 0.816 & 0.865 & 0.859 \\ 
Adjusted R$^{2}$ & 0.827 & 0.802 & 0.855 & 0.847 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 

## Ext5: Add an interaction term between “girls” and political parties.
```{r, results = 'hide'}
lm_ext5_105 <-lm(aauw ~ ngirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + ngirls*repub + factor(totchi) + factor(region) , data = datAAUW105)
lm_ext5_106 <-lm(aauw ~ ngirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + ngirls*repub + factor(totchi) + factor(region) , data = datAAUW106)
lm_ext5_107 <-lm(aauw ~ ngirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + ngirls*repub + factor(totchi) + factor(region) , data = datAAUW107)
lm_ext5_108 <-lm(aauw ~ ngirls + female + white + repub + age + age2 + srvlng + srvlng2 + rgroup + demvote + ngirls*repub + factor(totchi) + factor(region) , data = datAAUW108)

summary(lm_ext5_105)
summary(lm_ext5_106)
summary(lm_ext5_107)
summary(lm_ext5_108)
stargazer(lm_ext5_105, lm_ext5_106, lm_ext5_107, lm_ext5_108)
```

\begin{table}[!htbp] \centering 
  \caption{Impact of Number of Female Children on Legislator's Women's Issues Voting Record (including interaction b/w number of female children and party of legislator} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{AAUW} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Number of female children & 1.028 & 0.578 & 1.600 & 1.322 \\ 
  & (1.392) & (1.420) & (1.333) & (1.427) \\ 
  & & & & \\ 
 Number of female children$*$Republican & 2.652 & 2.176 & 1.729 & 1.888 \\ 
  & (1.611) & (1.674) & (1.613) & (1.732) \\ 
  & & & & \\ 
 Female & 9.206$^{***}$ & 10.351$^{***}$ & 7.529$^{***}$ & 6.705$^{**}$ \\ 
  & (2.904) & (2.880) & (2.617) & (2.736) \\ 
  & & & & \\ 
 White & 0.034 & 2.853 & $-$2.412 & 1.865 \\ 
  & (3.669) & (3.835) & (3.156) & (3.211) \\ 
  & & & & \\ 
 Republican & $-$63.478$^{***}$ & $-$58.468$^{***}$ & $-$65.210$^{***}$ & $-$65.951$^{***}$ \\ 
  & (2.919) & (3.044) & (2.820) & (3.059) \\ 
  & & & & \\ 
 Age & 0.837 & 2.061$^{**}$ & 1.292 & 2.344$^{***}$ \\ 
  & (0.858) & (0.901) & (0.799) & (0.861) \\ 
  & & & & \\ 
 Age squared & $-$0.006 & $-$0.019$^{**}$ & $-$0.011 & $-$0.021$^{***}$ \\ 
  & (0.008) & (0.008) & (0.007) & (0.008) \\ 
  & & & & \\ 
 Service Length & $-$0.168 & $-$0.717$^{*}$ & $-$0.084 & $-$0.145 \\ 
  & (0.324) & (0.380) & (0.346) & (0.326) \\ 
  & & & & \\ 
 Service Length squared & 0.003 & 0.025$^{*}$ & $-$0.001 & 0.005 \\ 
  & (0.011) & (0.013) & (0.011) & (0.010) \\ 
  & & & & \\ 
 No religion & 5.842 & 4.667 & 6.469 & $-$7.562 \\ 
  & (7.591) & (7.802) & (7.194) & (7.508) \\ 
  & & & & \\ 
 Catholic & $-$4.302$^{**}$ & $-$2.199 & $-$4.050$^{**}$ & $-$5.467$^{***}$ \\ 
  & (2.090) & (2.128) & (1.987) & (2.077) \\ 
  & & & & \\ 
 Other Christian & 2.689 & 1.525 & 1.730 & 3.912 \\ 
  & (4.983) & (4.910) & (4.491) & (4.683) \\ 
  & & & & \\ 
 Other religion & 9.815$^{**}$ & 11.757$^{***}$ & 10.143$^{***}$ & 3.203 \\ 
  & (4.040) & (4.340) & (3.787) & (3.959) \\ 
  & & & & \\ 
 Democratic vote in district & 63.228$^{***}$ & 58.599$^{***}$ & 56.980$^{***}$ & 67.677$^{***}$ \\ 
  & (11.562) & (12.041) & (9.119) & (10.907) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 434 & 434 & 434 & 433 \\ 
R$^{2}$ & 0.841 & 0.815 & 0.865 & 0.859 \\ 
Adjusted R$^{2}$ & 0.828 & 0.801 & 0.855 & 0.847 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 